\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-09 main.tex
Updates from Overleaf

This introduction to \SuperScreen is organized as follows: In Section~\ref{section:model}, we outline the model and its assumptions and in Section~\ref{section:implementation}, we describe its numerical implementation. In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package, highlighting notable functions, classes, and features, and discuss some important development details. In Section~\ref{section:examples}, we demonstrate how to perform a few simple types of simulations using \SuperScreen and compare the results to previous numerical and analytical solutions. Finally, in Section~\ref{section:conlusion}, we conclude by discussing applications, limitations, and possible extensions of the package.

@@

\subsection{Pearl vortices in thin films}
\label{section:examples:pearl-vortices}
Vortices trapped in 2D superconductors ($d\ll\lambda$, where $d$ is the film thickness and $\lambda$ is the London penetration depth), i.e. ``Pearl vortices'', are associated with different current and magnetic field distributions than Abrikosov vortices trapped in bulk type-II superconductors~\cite{Pearl1964-cl}. The 2D Fourier transform $\tilde{H}_z(\vec{k}, z)$ of the out-of-plane component of the magnetic field $H_z(\vec{r}, z)$ from a Pearl vortex located at the origin $x=y=z=0$ is given by

\begin{equation}
    \tilde{H}_z(\vec{k}, z)=\mathcal{F}\{H_z(\vec{r}, z)\}=\frac{1}{\mu_0}\frac{\Phi_0e^{-|\vec{k}||z|}}{1+2\Lambda|\vec{k}|},
    \label{eq:pearl}
\end{equation}
where $\mathcal{F}\{\cdot\}$ is the 2D Fourier transform, $\vec{k}=(k_x, k_y)$ are in-plane spatial frequencies, $z$ is the out-of-plane position at which the field is evaluated, and $2\Lambda = 2\lambda^2 / d$ is the Pearl length~\cite{Pearl1964-cl, Tafuri2004-ap}. The real-space magnetic field distribution near a Pearl vortex can be calculated numerically by taking the inverse Fourier transform of Equation~\ref{eq:pearl}: $H_z(\vec{r}, z)=\mathcal{F}^{-1}\{\tilde{H}_z(\vec{k}, z)\}$. The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figures XXX.

\begin{code}
\begin{minted}[fontsize=\small]{python}
# Create a device representing square thin film.
device = sc.Device(
    "film",
    layers=[sc.Layer("base", Lambda=0, z0=0)],
    films=[sc.Polygon("film", layer="base", points=sc.geometry.square(20))],
    # Add an abstract_polygon near the vortex position so that
    # that region will be meshed densely.
    abstract_regions=[
        sc.Polygon("circle", layer="base", points=sc.geometry.circle(0.1)),
    ],
    length_units="um",
)
device.make_mesh(min_triangles=8000)
# Specify the vortex position.
vortices = [sc.Vortex(x=0, y=0, layer="base")]
# Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
Lambdas = np.linspace(0, 1, 6) # [device.length_units]
solutions = []
for Lambda in Lambdas:
    device.layers["base"].Lambda = Lambda
    solution = sc.solve(
        device=device, vortices=vortices, field_units="Phi_0/um**2"
    )[-1]
    solutions.append(solution)
    # Use solution.field_at_position() to evaluate the magnetic field profile.
\end{minted}
\captionof{listing}{}
\label{code:pearl-vortex}
\end{code}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
    \caption{Caption}
    \label{fig:pearl}
\end{figure}

@@

There are several important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{Brandt2004-ew,Brandt2005-wj}. First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ less than film thickness $d$, such that the out-of-plane current density is approximately constant. There are cases where the model reproduces experimental results despite violation of this condition (e.g. the calculations and in Refs.~\cite{Kirtley2016-zz,Kirtley2016-gt}), but care must be taking in interpreting results in these cases. Second, as a London model, Brandt and Clem's method assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are well below the critical field and critical current density of all films in a device. 
% Third, while currents associated with vortices and flux trapped in holes can be modeled, \SuperScreen does not treat the energetics of vortex nucleation in films or fluxoid transitions in multiply-connected films. For further discussion of these topics in the context of the present model, see Refs.~\cite{Brandt2004-ew, Clem2005-ye}.
Third, as currently implemented, \SuperScreen does not support ``terminal currents,'' i.e. currents flowing in one terminal of a device and out another terminal. This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux (see Sections~\ref{section:model:holes} and~\ref{section:examples:mutual-inductance}). Terminal currents can be included in the stream function-base model by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}. Finally, care should be taken to ensure that for a given model the mesh is of sufficient density and quality that, to within the desired precision, the results of simulations do not depend on mesh size.

>>>>

This introduction to \SuperScreen is organized as follows: In Section~\ref{section:model}, we outline the model and its assumptions and in Section~\ref{section:implementation}, we describe its numerical implementation. In Section~\ref{section:overview}, we provide an overview of the structure of the \SuperScreen package and discuss some important development details. In Section~\ref{section:examples}, we demonstrate how to perform a few simple types of simulations using \SuperScreen and compare the results to previous numerical and analytical solutions. Finally, in Section~\ref{section:conlusion}, we conclude by discussing applications, limitations, and possible extensions of the package.

@@

\subsection{Pearl vortices in thin films}
\label{section:examples:pearl-vortices}
Vortices trapped in 2D superconductors ($d\ll\lambda$, where $d$ is the film thickness and $\lambda$ is the London penetration depth), i.e. ``Pearl vortices,'' are associated with different current and magnetic field distributions than Abrikosov vortices trapped in bulk type-II superconductors~\cite{Pearl1964-cl}. The 2D Fourier transform $\tilde{H}_z(\vec{k}, z)$ of the out-of-plane component of the magnetic field $H_z(\vec{r}, z)$ from a Pearl vortex located at the origin $x=y=z=0$ is given by

\begin{equation}
    \tilde{H}_z(\vec{k}, z)=\mathcal{F}\{H_z(\vec{r}, z)\}=\frac{1}{\mu_0}\frac{\Phi_0e^{-|\vec{k}||z|}}{1+2\Lambda|\vec{k}|},
    \label{eq:pearl}
\end{equation}
where $\mathcal{F}\{\cdot\}$ is the 2D Fourier transform, $\vec{k}=(k_x, k_y)$ are in-plane spatial frequencies, $z$ is the out-of-plane position at which the field is evaluated, and $2\Lambda = 2\lambda^2 / d$ is the Pearl length~\cite{Pearl1964-cl, Tafuri2004-ap}. The real-space magnetic field distribution near a Pearl vortex can be calculated numerically by taking the inverse Fourier transform of Equation~\ref{eq:pearl}: $H_z(\vec{r}, z)=\mathcal{F}^{-1}\{\tilde{H}_z(\vec{k}, z)\}$. The field distributions generated by \SuperScreen in the presence of vortices as described in Sections~\ref{section:model:vortices} and~\ref{section:implementation} agree to within a few percent with the distributions obtained using this Fourier transform method, as demonstrated in Code Block~\ref{code:pearl-vortex} and Figure~\ref{fig:pearl}.

\begin{code}
\begin{minted}[fontsize=\small]{python}
# Create a device representing square thin film.
device = sc.Device(
    "film",
    layers=[sc.Layer("base", Lambda=0, z0=0)],
    films=[sc.Polygon("film", layer="base", points=sc.geometry.square(20))],
    # Add an abstract_polygon near the vortex position so that
    # that region will be meshed densely.
    abstract_regions=[
        sc.Polygon("circle", layer="base", points=sc.geometry.circle(0.1)),
    ],
    length_units="um",
)
device.make_mesh(min_triangles=8000)
# Specify the vortex position.
vortices = [sc.Vortex(x=0, y=0, layer="base")]
# Sweep Lambda, solve the model, and evaluate the field at the given coordinates.
Lambdas = np.linspace(0, 1, 6) # [device.length_units]
solutions = []
for Lambda in Lambdas:
    device.layers["base"].Lambda = Lambda
    solution = sc.solve(
        device=device, vortices=vortices, field_units="Phi_0/um**2"
    )[-1]
    solutions.append(solution)
    # Use solution.field_at_position() to evaluate the magnetic field profile.
\end{minted}
\captionof{listing}{Calculates the magnetic field distribution near a vortex trapped in a uniform superconducting film as a function of the film's effective penetration depth, $\Lambda$ (see Figure~\ref{fig:pearl}).}
\label{code:pearl-vortex}
\end{code}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{examples/images/pearl.pdf}
    \caption{Vortex field profiles calculated with \SuperScreen agree to within a few percent with the analytical solution (Eq.~\ref{eq:pearl}). (a) Cross section along the $x$-axis of the out-of-plane magnetic field $\mu_0H_z$ from a vortex located at the origin, $x=y=z=0\,\mu\mathrm{m}$ in a superconducting film, evaluated at a vertical distance $z=1\,\mu\mathrm{m}$ above the film for several different effective penetration depths $\Lambda$. (b) Cross-section along the $z$-axis of $\mu_0H_z$ from a vortex located at the origin, evaluated at $x=y=0\,\mu\mathrm{m}$, directly above the center of the vortex (logarithmic $y$ axis scale). In (a) and (b), the results from \SuperScreen are shown as open circles and the results from the Fourier transform method are shown as solid lines. (c) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $x$-axis cut shown in (a). (d) Percentage difference between the $\mu_0H_z$ calculated with \SuperScreen and the Fourier transform method for the $z$-axis cut shown in (b).}
    \label{fig:pearl}
\end{figure}

@@

There are several important limitations to the applicability of \SuperScreen and the matrix inversion method on which it is based~\cite{Brandt2004-ew,Brandt2005-wj}. First, strictly speaking all superconducting films should be in the 2D limit, with London penetration depth $\lambda$ less than film thickness $d$, such that the out-of-plane current density is approximately constant. There are cases where the model reproduces experimental results despite violation of this condition (e.g. the calculations and in Refs.~\cite{Kirtley2016-zz,Kirtley2016-gt}), but care must be taking in interpreting results in these cases. Second, as a London model, Brandt and Clem's method assumes that all superconducting films behave linearly and without dissipation, and that the applied magnetic field and current density are well below the critical field and critical current density of all films in a device. 
% Third, while currents associated with vortices and flux trapped in holes can be modeled, \SuperScreen does not treat the energetics of vortex nucleation in films or fluxoid transitions in multiply-connected films. For further discussion of these topics in the context of the present model, see Refs.~\cite{Brandt2004-ew, Clem2005-ye}.
Third, as currently implemented, \SuperScreen does not support ``terminal currents,'' i.e. currents flowing in one terminal of a device and out another terminal. This means that inductance calculations are limited to structures with holes, in which all applied currents are circulating currents associated with trapped flux (see Sections~\ref{section:model:holes} and~\ref{section:examples:mutual-inductance}). Terminal currents can be included in the stream function-base model by setting appropriate boundary conditions~\cite{Khapaev1997-kw,Khapaev2001-xq,Khapaev2001-pw,Muller2021-ci}. Finally, care should be taken to ensure that for a given model the mesh is of sufficient density that, to within the desired precision, the results of simulations do not depend on mesh size.
